---
title: "HW1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HW1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggplot2)
```

## Question 0

### Question 0A
Amy

### Question 0B
I have read and understood the entire syllabus

### Question 0C
I have taken BIOST 514/515 which use R for homework assigments. I am relatively comfortable using R. 

### Question 0D
I hope to be more comfortable with using R. 

## Question 1 

## Question 2

```{r}
source("https://raw.githubusercontent.com/linnykos/561_s2024_public/main/homework1/generate_data.R")
```

### Question 2A
- The input is an integer n. The output is a list of n random generated numbers from either a normal(10,1), gamma(2,2) or chisq(3) distribution. 

### Question 2B
```{r}
sample_size <- c(1, 2, 3, 5, 10, 100)

par(mfrow = c(2, 3))
for(n in sample_size){
  data <- c()
  for(i in 1:1000){
    x <- mean(generate_data(n))
    data <- c(data, x)
  }
  hist(data, breaks=100, main = paste("Sample Size: ", n))
}
```

### Question 2C
The plots help verify the CLT because as sample size gets larger, the distribution appears to resemble a standard normal curve more closely. 

## Question 3

```{r}
df <- read.csv("https://raw.githubusercontent.com/linnykos/561_s2024_public/main/homework1/sea-ad.csv")

head(df)

summary(df)
```

### Question 3A
head(df) displays all columns of df for the first 6 rows. summary(df) provides descriptive statistics for each column (ie num of observations, min, max, quartiles, mean, median, etc.). 

### Question 3B

```{r}
dim(df)
class(df)
```

### Question 3C

```{r}
df$Age.at.Death <- sapply(df$Age.at.Death, function(x) if(x == '90+') {90} else {as.double(x)})
hist(df$Age.at.Death, main = "Histogram of Donor Age")
```

### Question 3D

```{r}
df$Sex <- as.factor(df$Sex)
df$APOE4.Status <- as.factor(df$APOE4.Status)
df$Cognitive.Status <- as.factor(df$Cognitive.Status)
df$Braak <- as.factor(df$Braak)
```

### Question 3E

```{r}
summary(df)
```
This summary provides counts of how many observations are in each unique category in the variables that we just converted to factors. 
### Question 3F

```{r}
table(df$Braak, df$Cognitive.Status)
```
### Question 3G

```{r}
table(cut(df$Last.CASI.Score, breaks = quantile(df$Last.CASI.Score, na.rm = TRUE)), df$Cognitive.Status)
```
It appears that lower CASI scores are associated with dementia, while high CASI scores are associated with no dementia. 

## Question 4

## Question 5
